\section{Peer-Reviewed Journal Publications}

\jpub{%
    P. Nepal, \textbf{A. A. Bashit}, [4 authors], and L. Makowski, \textcolor{black}{``Scanning X-ray microdiffraction studies of protein accumulation and tissue loss in thin sections of human brain tissue in Alzheimer's disease,''} \textit{submitted}, May 2026, arXiv preprint pending.%
}
\jpub{%
    \textbf{A. A. Bashit}, P. Nepal, and L. Makowski, \href{https://arxiv.org/abs/2511.12451}{\textcolor{black}{``A Multicollinearity-Aware Signal-Processing Framework for Cross-$\beta$ Identification via X-ray Scattering of Alzheimer's Tissue,''}} \textit{under review}, Nov. 2025. [Preprint: \href{https://arxiv.org/pdf/2511.12451}{arXiv}]%
}
\jpub{%
    P. Nepal, \textbf{A. A. Bashit}, and L. Makowski, \href{https://journals.iucr.org/j/issues/2024/05/00/ge5158/ge5158.pdf}{\textcolor{black}{``Characterization of sub-micrometre-sized voids in fixed human brain tissue using scanning X-ray microdiffraction,''}} \textit{Journal of Applied Crystallography (IUCr)}, Oct. 2024.%
}
\jpub{%
    P. Nepal, \textbf{A. A. Bashit}, L. Yang, and L. Makowski, \href{https://journals.iucr.org/j/issues/2022/06/00/fs5212/fs5212.pdf}{\textcolor{black}{``Small-angle X-ray microdiffraction from fibrils embedded in tissue thin sections,''}} \textit{Journal of Applied Crystallography (IUCr)}, Dec. 2022.%
}
\jpub{%
    J. Martinez-Lorenzo, J. Hudack, Y. Jing, M. Shaham, Z. Liang, \textbf{A. A. Bashit}, [5 authors], and A. Fox, \href{https://doi.org/10.3390/robotics11050094}{\textcolor{black}{``Preliminary Experimental Results of Context-Aware Teams of Multiple Autonomous Agents Operating under Constrained Communications,''}} \textit{Robotics}, Sep. 2022.%
}
\jpub{%
    \textbf{A. A. Bashit}, P. Nepal, T. Connors, D. H. Oakley, B. T. Hyman, L. Yang, and L. Makowski, \href{https://doi.org/10.3389/fnins.2022.909542}{\textcolor{black}{``Mapping the Spatial Distribution of Fibrillar Polymorphs in Human Brain Tissue,''}} \textit{Frontiers in Neuroscience}, May 2022.%
}
\jpub{%
    F. S. Saeed, \textbf{A. A. Bashit}, V. Viswanathan, and D. Valles, \href{https://doi.org/10.3390/app11188425}{\textcolor{black}{``An Initial Machine Learning-Based Victim’s Scream Detection Analysis for Burning Sites,''}} \textit{Applied Sciences}, Sep. 2021.%
}
\jpub{%
    M. R. Islam, G. K. Beng, and \textbf{A. A. Bashit}, \href{https://www.ajbasweb.com/old/ajbas/2014/Special\%2012/123-126.pdf}{\textcolor{black}{``Design and Fabrication of Segment Display Architecture for Displaying Bengali and English Numerals,''}} \textit{Australian Journal of Basic and Applied Sciences (AJBAS)}, Nov. 2014.%
}
\jpub{%
    A. A. Mansur, \textbf{A. A. Bashit}, M. R. Islam, \href{https://research.ijais.org/volume5/number4/ijais12-450889.pdf}{\textcolor{black}{``Harmonic Analysis of Front-End Current of Three-Phase Single-Switch Boost Converter,''}} \textit{International Journal of Applied Information Systems (IJAIS)}, Mar. 2013.%
}

