\section{Teaching}

\cvitem{Apr 2026}{%
    \textbf{Guest Lecturer}, Bioengineering, Northeastern University, Boston, MA. \\[0.3em]
    BIOE 5410: Molecular Bioengineering (Host: \href{https://makowski-lab.sites.northeastern.edu/}{Prof. Lee Makowski}) – Delivered a guest lecture on machine learning for drug discovery to an audience of 52 undergraduate, M.S., and Ph.D. students.%
}
\cvitem{Sep 2020--Dec 2020}{%
    \textbf{Teaching Assistant}, Northeastern University, Boston, MA. \\[0.3em]
    EECE 2323: Fundamentals of Digital Design and Computer Organization – Led recitation lectures and designed/conducted laboratory experiments for a class of approximately $40$ undergraduate students.%
}
\cvitem{Aug 2017--Dec 2017}{%
    \textbf{Graduate Instructional Assistant}, Texas State University, San Marcos, TX. \\[0.3em]
    MFGE 4392/4394: Microelectronics Manufacturing I/II – Supervised cleanroom laboratories on full CMOS-compatible semiconductor device fabrication (wafer preparation through final test) for a class of approximately $20$ undergraduate students.%
}
\cvitem{Feb 2012--Mar 2014}{%
    \textbf{Lecturer}, Prime University, Dhaka, Bangladesh. \\[0.3em]
    Delivered classroom lectures, designed and graded exams, supervised labs, and held office hours for classes of approximately $20$–$80$ undergraduate students. 
    \begin{itemize}
        \item EEE 157: Electrical Circuit II (Fall 2012)
        \item EEE 210: Electronic Circuit Simulation Lab (Spring 2012)
        \item EEE 235: Energy Conversion I (Summer 2012)
        \item EEE 325: Energy Conversion II (Summer 2012, Spring 2013)
        \item EEE 326: Energy Conversion II Lab (Spring 2013)
        \item EEE 407: Microprocessor Systems and Interfacing (Spring 2012)
        \item EEE 425: Power System I (Summer 2012, Spring 2013)
        \item EEE 431: Power System II (Fall 2012)
        \item EEE 473: Power System Protection (Fall 2012)
    \end{itemize}%
}