\section{Education}

\cvitem{Jul 2019--Dec 2024}{%
    \textbf{Northeastern University, Boston, MA, USA} \\ {Ph.D. in Electrical Engineering} \\
    % \textit{Concentration:} {Communications, Control \& Signal Processing} \\
    \textit{Thesis:} \href{https://www.proquest.com/openview/56709cfe70caac13aec1ad921ea03497/1?pq-origsite=gscholar&cbl=18750&diss=y}{\textcolor{black}{Structural Characterization of Pathological Inclusions in Human Brain Tissue with Alzheimer's Disease}}.
    
    \textit{Advisor:} \href{https://makowski-lab.sites.northeastern.edu/}{Prof. Lee Makowski}
}

\cvitem{Aug 2017--Aug 2019}{%
    \textbf{Texas State University, San Marcos, TX, USA}  \\
    {M.Sc. in Engineering (Electrical Engineering)} \\
    % \textit{Concentration:} {Electrical Engineering} \\
    \textit{Thesis:} \href{https://hdl.handle.net/10877/8384}{\textcolor{black}{A Comprehensive Solar Powered Remote Monitoring and Identification of Houston Toad Call Automatic Recognizing Device System Design}}. \\
    \textit{Advisors:} \href{https://damian.wp.txstate.edu/about/}{Prof. Damian Valles} and \href{https://www.bio.txst.edu/faculty-staff/michael-forstner.html}{Prof. Michael Forstner}
}

\cvitem{Feb 2007--Jul 2011}{%
    \textbf{Rajshahi University of Engineering \& Technology (RUET), Bangladesh} \\
    {B.Sc. in Electrical \& Electronic Engineering} \\
    \textit{Thesis:} Study of wavelength dependence of refractive index and material dispersion of various materials. \\
    \textit{Advisors:} {Prof. S.M. Abdur Razzak} and {Prof. Md. Shahidul Islam}
    % \href{https://www.ruet.ac.bd/sma.razzak}
    % \href{https://www.ruet.ac.bd/siruet}
}