\section{Research Experience}

\cvitem{Jan 2025--present}{%
    \textbf{Postdoctoral Research Associate}, \textit{Bioengineering, Northeastern University}.
    
    Advisor: \href{https://makowski-lab.sites.northeastern.edu/}{Prof. Lee Makowski}
    
    \textbf{Statistical methods for X-ray scattering analysis.}
    
    Formulating mathematical frameworks for tissue signal extraction and creating Python packages for large-scale X-ray microdiffraction analysis.
}

\cvitem{Oct 2020--Dec 2024}{%
    \textbf{Graduate Research Assistant}, \textit{Bioengineering, Northeastern University}.
    
    Advisor: \href{https://makowski-lab.sites.northeastern.edu/}{Prof. Lee Makowski}
    
    \textbf{Machine learning for Alzheimer's disease pathology characterization.}
    
    Applied supervised and unsupervised learning models for analyzing X-ray microdiffraction data from human brain tissue. Implemented image registration and quantitative models for structural correlation analysis.
}

\cvitem{Sep 2022--Dec 2022}{%
    \textbf{Visiting Graduate Student}, \textit{Biological Chemistry and Molecular Pharmacology, Harvard Medical School}.
    
    Host: \href{https://crystal.harvard.edu/stephen-c-harrison/}{Prof. Stephen C. Harrison}
    
    \textbf{Cryo-EM tomography automation.}
    
    Created Python GUI interface for automated data collection procedures in the cryo-EM center.
}

\cvitem{Jul 2019--Aug 2020}{%
    \textbf{Graduate Research Assistant}, \textit{Electrical \& Computer Engineering, Northeastern University}.
    
    Advisor: \href{https://coe.northeastern.edu/people/martinez-lorenzo-jose/}{Prof. José A. Martínez-Lorenzo}
    
    \textbf{Autonomous drone swarm coordination.}
    
    Built and programmed customized drones with neural network capabilities. Engineered control systems integrating embedded computers and flight controllers.
}

\cvitem{Jan 2018--Jun 2019}{%
    \textbf{Graduate Research Assistant}, \textit{Electrical Engineering, Texas State University}.
    
    Advisor: \href{https://damian.wp.txstate.edu/about/}{Dr. Damian Valles}
    
    \textbf{Embedded system for wildlife monitoring.}
    
    Designed solar-powered system for real-time Houston Toad detection using neural networks and audio signal processing.
}